\begin{thebibliography}{99}

\bibitem{adomavicius2005toward}
G. Adomavicius and A. Tuzhilin, “Toward the next generation of recommender systems: A survey of the state-of-the-art and possible extensions,” \textit{IEEE Transactions on Knowledge and Data Engineering}, vol. 17, no. 6, pp. 734–749, 2005. [Online]. Available: https://doi.org/10.1109/TKDE.2005.99

\bibitem{su2009survey}
X. Su and T. M. Khoshgoftaar, “A survey of collaborative filtering techniques,” \textit{Advances in Artificial Intelligence}, vol. 2009, p. 421425, 2009.

\bibitem{koren2009matrix}
Y. Koren, R. Bell, and C. Volinsky, “Matrix factorization techniques for recommender systems,” \textit{Computer}, vol. 42, no. 8, pp. 30–37, 2009.

\bibitem{rendle2010factorization}
S. Rendle, “Factorization machines,” in \textit{2010 IEEE International Conference on Data Mining}. IEEE, 2010, pp. 995–1000.

\bibitem{strunk1979style}
W. Strunk, Jr. and E. B. White, \textit{The Elements of Style}, 3rd ed. Macmillan, 1979.

\bibitem{bellucci2004integrating}
E. Bellucci, A. Lodder, and J. Zeleznikow, “Integrating artificial intelligence, argumentation and game theory to develop an online dispute resolution environment,” in \textit{16th International Conference on Tools with Artificial Intelligence}. IEEE, 2004, pp. 749–754.

\bibitem{antoniou2007drbrokering}
G. Antoniou, T. Skylogiannis, A. Bikakis, M. Doerr, and N. Bassiliades, “Dr-brokering: A semantic brokering system,” \textit{Knowledge-Based Systems}, vol. 20, no. 1, pp. 61–72, 2007.

\bibitem{russell2009ai}
S. J. Russell, P. Norvig, J. F. Canny, J. M. Malik, and D. D. Edwards, \textit{Artificial intelligence: a modern approach}, 3rd ed. Prentice Hall, 2009, vol. 2.

\bibitem{ajax_tutorial}
“Ajax Tutorial,” http://www.tutorialspoint.com/ajax/ [Accessed 2021.03.10]. [Online]. Available: http://www.tutorialspoint.com/ajax/.

\bibitem{mcauley2015image}
J. McAuley, C. Targett, Q. Shi, and A. van den Hengel, “Image-based recommendations on styles and substitutes,” in \textit{Proceedings of the 38th International ACM SIGIR Conference on Research and Development in Information Retrieval}, 2015, pp. 43–52.

\bibitem{ronneberger2015unet}
O. Ronneberger, P. Fischer, and T. Brox, “U-Net: Convolutional Networks for Biomedical Image Segmentation,” in \textit{Medical Image Computing and Computer-Assisted Intervention (MICCAI)}, vol. 9351, Springer, 2015, pp. 234–241.

\bibitem{qin2020u2net}
X. Qin, Z. Zhang, C. Huang, M. Dehghan, O. R. Zaiane, and M. Jagersand, “U2-Net: Going Deeper with Nested U-Structure for Salient Object Detection,” \textit{Pattern Recognition}, vol. 106, p. 107404, 2020.

\bibitem{han2017learning}
X. Han, Z. Wu, Y. G. Jiang, and L. S. Davis, “Learning Fashion Compatibility with Bidirectional LSTMs,” in \textit{Proceedings of the 25th ACM International Conference on Multimedia}, 2017, pp. 1078–1086.

\bibitem{flask_doc}
Flask Documentation. [Online]. Available: https://flask.palletsprojects.com/

\bibitem{reactnative_doc}
React Native Documentation. [Online]. Available: https://reactnative.dev/

\bibitem{rembg_tool}
Daniel Gatis, “Rembg - Background Removal Tool,” GitHub Repository. [Online]. Available: https://github.com/danielgatis/rembg

\bibitem{lecun2015deep}
Y. LeCun, Y. Bengio, and G. Hinton, "Deep learning," \textit{Nature}, vol. 521, no. 7553, pp. 436-444, 2015.

\bibitem{goodfellow2016deep}
I. Goodfellow, Y. Bengio, and A. Courville, \textit{Deep Learning}. MIT Press, 2016.

\bibitem{he2016deep}
K. He, X. Zhang, S. Ren, and J. Sun, "Deep Residual Learning for Image Recognition," in \textit{Proceedings of the IEEE Conference on Computer Vision and Pattern Recognition (CVPR)}, 2016, pp. 770-778.

\bibitem{tan2019efficientnet}
M. Tan and Q. V. Le, "EfficientNet: Rethinking Model Scaling for Convolutional Neural Networks," in \textit{International Conference on Machine Learning (ICML)}, 2019, pp. 6105-6114.

\bibitem{redmon2016you}
J. Redmon, S. Divvala, R. Girshick, and A. Farhadi, "You Only Look Once: Unified, Real-Time Object Detection," in \textit{Proceedings of the IEEE Conference on Computer Vision and Pattern Recognition (CVPR)}, 2016, pp. 779-788.

\bibitem{vaswani2017attention}
A. Vaswani et al., "Attention Is All You Need," in \textit{Advances in Neural Information Processing Systems}, 2017, pp. 5998–6008.

\bibitem{chollet2017xception}
F. Chollet, "Xception: Deep Learning with Depthwise Separable Convolutions," in \textit{Proceedings of the IEEE Conference on Computer Vision and Pattern Recognition (CVPR)}, 2017, pp. 1251-1258.

\bibitem{kingma2014adam}
D. P. Kingma and J. Ba, "Adam: A Method for Stochastic Optimization," in \textit{International Conference on Learning Representations (ICLR)}, 2015.

\bibitem{srivastava2014dropout}
N. Srivastava, G. Hinton, A. Krizhevsky, I. Sutskever, and R. Salakhutdinov, "Dropout: A Simple Way to Prevent Neural Networks from Overfitting," \textit{Journal of Machine Learning Research}, vol. 15, pp. 1929-1958, 2014.

\end{thebibliography}
